Predicting sales of newly published books

### 2015-08-21 paper.tex
completando el estado del arte

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where there is historical data available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.

>>>>

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
Proposed method is suitable in those sales forecasting problems with abundant 
online reviews and historical data.
